Ecological validity of detecting data fabrication in experimental studies.

### 2016-04-25 submission/manuscript.Rmd
Add osf link to qualtrics questions
Add separate sets of sampling frames study 1 (for qualtrics batch mailing)

---
title: "Ecological validity of detecting data fabrication in experimental studies."
author: "Chris HJ Hartgerink"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: word_document
csl: ../bibliography/apa.csl
bibliography: ../bibliography/library.bib
---
<!---

@@

Upon completing the fabrication of the data, participants were debriefed. Several questions were asked about their statistical knowledge and approach to data fabrication, and they were reminded that data fabrication is widely condemned by professional organizations, institutions, and funding agencies alike. The full set of questions from the study are available at osf.io/XXXX.

>>>>

---
title: "Ecological validity of detecting data fabrication in experimental studies."
author: "Chris HJ Hartgerink"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: pdf_document
csl: ../bibliography/apa.csl
bibliography: ../bibliography/library.bib
---
<!---

@@

Upon completing the fabrication of the data, participants were debriefed. Several questions were asked about their statistical knowledge and approach to data fabrication, and they were reminded that data fabrication is widely condemned by professional organizations, institutions, and funding agencies alike. The full set of questions from the study are available at osf.io/w984b.
